Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-10-23 main.tex
Update text
Update main.tex

A.M.K. implemented the {\it Databank layer} and NMRlipids Databank-API.
H.S.A. contributed to the quality evaluation metrics based on NMR and X-ray scattering form factors, wrote the machine learning code, and was involved in testing the GUI, polishing the manuscript, and in community outreach to source additional data.
L.S.B. implemented roughly 630 pre-existing lipid bilayer simulations into the Databank and created the corresponding mapping files.
P.B. implemented the PCA-based equilibration metric, supervised the work of A.K., and participated in code refactoring.
F.F.-R. set up and performed simulations with Slipids Force Field: ID 617, ID 207 and ID 82. 
T.M.F. performed and analysed the solid-state NMR experiments.
P.F.J.F. contributed to changes in the buildH software so that the Databank can handle united atom simulation data.
R.G.-F. was responsible for the design, validation and supervision of the back-end and front-end for the graphical user interface (GUI) development (databank.nmrlipids.fi).
I.G. advised on implementation of the PCA-based equilibration metric and supervised the work of A.K.
B.K. contributed to the initial design and implementation of the Databank and was involved with writing the manuscript.
N.K. contributed experimental scattering data. % and SIMtoEXP algorithm.
P.K. Implemented the flip-flop analysis and supported the integration of PCA equilibration metric into the databank.
M.K. provided simulations with the OPLS3e force field. 
A.K. implemented the PCA-based equilibration metric.
A.L. provided simulations of heterogeneous lipid membranes including sphingolipids and glycosphingolipids with CHARMM36 force field.
F.S.-L. developed the back-end and participated in the design and development and validation of the graphical user interface (GUI) (databank.nmrlipids.fi).
F.L. provided simulations using the CHARMM36m forcefield, incorporating cholesterol POPC and SAPI25 lipids.
J.J.M. provided simulations with the Amber force field, general discussion, and manuscript editing.
M.S.M supported O.H.S.O. in conceptualising the project, contributed to the quality evaluation metrics based on NMR and X-ray scattering form factors, assisted in refining the manuscript and the GUI, and guided the work of L.S.B. and M.K.
C.M. worked on the databank implementation and contributed code improvements.
L.M. performed simulations (for sphingomyelin, CHARMM36 force field, and Orange force field)
R.N. implemented the code for the calculations of X-ray scattering form factors.
A.N. provided simulations with TLCL lipid, simulations with Reaction-Field instead of PME, and improved the implementation.
T.J.P. performed many of the all-atom and united-atom simulations and contributed to discussions on the project.
A.P. was responsible for the design, validation and supervision of the back-end and front-end for the graphical user interface (GUI) development (databank.nmrlipids.fi).
S.S. contributed simulations of heterogeneous lipid membranes including sphingomyelin and ceramides with CHARMM36 force field.
R.T. Provided simulations of complex lipid-bilayers with charmm36m force field.
N.R. contributed simulations of complex lipid-bilayers obtained with NAMD and the charmm36 force field
O.H.S.O. designed and supervised the work, implemented the water permeation, diffusion and machine learning analyses, and wrote the manuscript.

>>>>

A.M.K. implemented the {\it Databank layer} and NMRlipids Databank-API.
H.S.A. contributed to the quality evaluation metrics based on NMR and X-ray scattering form factors, wrote the machine learning code, and was involved in testing the GUI, polishing the manuscript, and in community outreach to source additional data.
L.S.B. implemented roughly 630 pre-existing lipid bilayer simulations into the Databank and created the corresponding mapping files.
P.B. implemented the PCA-based equilibration metric, supervised the work of A.K., and participated in code refactoring.
F.F.-R. set up and performed simulations with Slipids Force Field: ID 617, ID 207 and ID 82. 
T.M.F. performed and analysed the solid-state NMR experiments.
P.F.J.F. contributed to changes in the buildH software so that the Databank can handle united atom simulation data.
R.G.-F. was responsible for the design, validation and supervision of the back-end and front-end for the graphical user interface (GUI) development (databank.nmrlipids.fi).
I.G. advised on implementation of the PCA-based equilibration metric and supervised the work of A.K.
B.K. contributed to the initial design and implementation of the Databank and was involved with writing the manuscript.
N.K. contributed experimental scattering data. % and SIMtoEXP algorithm.
P.K. Implemented the flip-flop analysis and supported the integration of PCA equilibration metric into the databank.
M.K. provided simulations with the OPLS3e force field. 
A.K. implemented the PCA-based equilibration metric.
A.L. provided simulations of heterogeneous lipid membranes including sphingolipids and glycosphingolipids with CHARMM36 force field.
F.S.-L. developed the back-end and participated in the design and development and validation of the graphical user interface (GUI) (databank.nmrlipids.fi).
F.L. provided simulations using the CHARMM36m force field, incorporating cholesterol POPC and SAPI25 lipids.
J.J.M. provided simulations with the Amber and CHARMM36m force fields, general discussion, and manuscript editing.
M.S.M supported O.H.S.O. in conceptualising the project, contributed to the quality evaluation metrics based on NMR and X-ray scattering form factors, assisted in refining the manuscript and the GUI, and guided the work of L.S.B. and M.K.
C.M. worked on the databank implementation and contributed code improvements.
L.M. performed simulations (for sphingomyelin, CHARMM36 force field, and Orange force field)
R.N. implemented the code for the calculations of X-ray scattering form factors.
A.N. provided simulations with TLCL lipid, simulations with Reaction-Field instead of PME, and improved the implementation.
T.J.P. performed many of the all-atom and united-atom simulations and contributed to discussions on the project.
A.P. was responsible for the design, validation and supervision of the back-end and front-end for the graphical user interface (GUI) development (databank.nmrlipids.fi).
S.S. contributed simulations of heterogeneous lipid membranes including sphingomyelin and ceramides with CHARMM36 force field.
R.T. Provided simulations of complex lipid-bilayers with charmm36m force field.
N.R. contributed simulations of complex lipid-bilayers obtained with NAMD and the charmm36 force field
O.H.S.O. designed and supervised the work, implemented the water permeation, diffusion and machine learning analyses, and wrote the manuscript.
